---
title: "Feature Selection"
author: "ROTICH HARON"
date: "2/10/2022"
output: html_document
---

---
##understanding the context
#Carrefour Kenya  is one of the leading reatailsalers in the country and would like to know the most relevant strategies to put in place in order to  increase its sales. The marketing departmennt have trouble  in developing  these strategies, but working in partnership with data analyst will help alot in getting important insights from data and make informes strategies.

#Sucess metrics
# the sucess of this will be achived by performing dimensuionality reduction to help in aunderstanding the data behaviour.

# loading data
```{r}
#install.packages("tidyverse")
library(tidyverse)
```
```{r}
#data = url("Supermarket_Dataset_1_Sales_Data <- #read_csv("C:/Users/hp/Downloads/Supermarket_Dataset_1 - Sales Data.csv")")
df<- read_csv("C:/Users/hp/Downloads/Supermarket_Dataset_1 - Sales Data.csv")

```
#preview data
```{r}
head(df)
```
#checking for shape
```{r}
str(df)
```
# check number of trecords
```{r}
dim(df)
# our data has  1000 rows and columns
```
# summary of data
```{r}
summary(df)
```
# Data cleansing
## checkinfor missing values
```{r}
sum(is.na(df))
# there are no missing values thus no action taken
```
# checking for duplicates
```{r}
sum(duplicated(df))
# there were no duplicates identified
```
# outlier detection using boxplots
```{r}
boxplot(df$`Unit price`)
# unit price variables have no outliers
```
```{r}
boxplot(df$Tax)
# Tax variable has a few outliers
```
```{r}
boxplot(df$Quantity)
# quanntity variable has no outliers
```
```{r}
boxplot(df$Time)
# there are no outliers in time column
```
```{r}
boxplot(df$cogs)
# there are  a few outliers  in the cogs variable
```
```{r}
boxplot(df$`gross margin percentage`)

# no ouliers in gross marginpercentage variable
```
```{r}
boxplot(df$`gross income`)
# gross income variable has  some outliers
```
```{r}
boxplot(df$Rating)
# ratings variables has no outliers

```
```{r}
boxplot(df$Total)
# totals vaiable has a numberof uoutliers 
```
# univariate analysis
```{r}
#measures of central tendecies
summary(df)

```
# checkinfor distribution
```{r}
# using density plots
plot(density(df$`Unit price`))
#
```
```{r}
plot(density(df$Tax))
```
```{r}
plot(hist(df$`Unit price`))

```
```{r}
plot(hist(df$Rating))
```
```{r}
plot(density(df$`gross margin percentage`))


```
```{r}
plot(hist(df$`gross income`))

```
```{r}
plot(density(df$Total))

```
# Bivariate analysis
## correlation
```{r}
# to extract numeric columns
num_cols <- unlist(lapply(df, is.numeric))         # Identify numeric columns
num_cols

```
```{r}
# creating data frame for numeric columns
df_num <- df[ , num_cols]                        # Subset numeric columns of data
df_num

```
```{r}
# correlation matrix
# corr functions 
cor(df_num, method = c("pearson", "kendall", "spearman"))
res <- cor(df_num)
round(res, 2)


```
# scatter plots
```{r}
plot(df$`Unit price`, df$Total, pch=16, col='steelblue',
     main='Unit Price vs. Total',
     xlab='Unit Price', ylab='Total')

```

```{r}
plot(df$Quantity, df$Total, pch=16, col='steelblue',
     main='Quantity vs. Total',
     xlab='Quantity', ylab='Total')

```
```{r}
plot(df$Tax, df$Total, pch=16, col='steelblue',
     main='Tax vs. Total',
     xlab='Tax', ylab='Total')

```
```{r}
plot(df$cogs, df$Total, pch=16, col='steelblue',
     main='cogs vs. Total',
     xlab='Cogs', ylab='Total')

```
```{r}
plot(df$`gross margin percentage`, df$Total, pch=16, col='steelblue',
     main='Quantity vs. Total',
     xlab='Quantity', ylab='Total')

```
```{r}
plot(df$`gross income`, df$Total, pch=16, col='steelblue',
     main='gross income vs. Total',
     xlab='gross income', ylab='Total')

```
```{r}
plot(df$Rating, df$Total, pch=16, col='steelblue',
     main='Ratingvs. Total',
     xlab='Rating', ylab='Total')
```

# Data preprocessing
```{r}
# dropping unnecessary columns
df = subset(df, select = -c(`Invoice ID`,Time,Date) )
```
# label encoding
```{r}
# label encoding
#install.packages("caret")
library(caret)
```

```{r}
#df$Branch <- ifelse(df$Branch == "Satisfactory",1,0)
#df$`Customer type`<- ifelse(df$`Customer type`== "Satisfactory",1,0)
#df$Gender <- ifelse(df$Gender == "Satisfactory",1,0)
#df$`Product line`<- ifelse(df$`Product line` == "Satisfactory",1,0)
#df$Payment <- ifelse(df$Payment == "Satisfactory",1,0)

#table(df$Payment)

```
```{r}
# checking if label encoding is implemented
head(df)
```

#FEATURE SELECTION
###Filter methods
```{r}
# Installing and loading our mclust package
#loading lbraries
library(caret)
library(corrplot)
colnames(df_num)

```

```{r}
suppressWarnings(
        suppressMessages(if
                         (!require(mclust, quietly=TRUE))
                install.packages("mclust")))
library(mclust)
```

```{r}

# Calculating the correlation matrix
# ---
#
correlationMatrix <- cor(df_num)
````
```{r}

# Find attributes that are highly correlated
# ---
#
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.75)
```

```{r}
# Highly correlated attributes
# 
highlyCorrelated

names(df[,highlyCorrelated])
```
```{r}

# Removing Redundant Features 
# ---
# 
df2<-df[-highlyCorrelated]
df2
```

```{r}
# Performing our graphical comparison
# ---
# 
#par(mfrow = c(1, 2))
#corrplot(correlationMatrix, order = "hclust")
#corrplot(cor(df2), order = "hclust")
# Performing our graphical comparison

```
#

## Wrapper method
```{r}
#Installing and loading our clustvarsel package
# 
suppressWarnings(
        suppressMessages(if
                         (!require(clustvarsel, quietly=TRUE))
                install.packages("clustvarsel")))
                         
library(clustvarsel)
```

```{r}
#Installing and loading our mclust package
# 
suppressWarnings(
        suppressMessages(if
                         (!require(mclust, quietly=TRUE))
                install.packages("mclust")))
library(mclust)
```

```{r}
# building the clustering model:
#Subset1 = df_num[,out$subset]
#mod = Mclust(Subset1, G = 1:5)
#summary(mod)

```
```{r}
#plot(mod,c("classification"))
````

## Using Embedded Methods
```{R}
library(wskm)
df1 <- df_num[,apply(df_num, 2, var, na.rm=TRUE) != 0]
df1=prcomp(df1)
model <- ewkm(df_num[1:4], 3, lambda=2, maxiter=1000)
```

```{r}
# Cluster Plot against 1st 2 principal components
library("cluster")
clusplot(df_num[1:4], model$cluster, color=TRUE, shade=TRUE,
         labels=2, lines=3,main='Cluster Analysis for Iris')

```
```{r}
#checking weights
round(model$weights*100,2)

````

