---
title: "ANOMALY DETECTION"
author: "ROTICH HARON"
date: "2/5/2022"
output: html_document
---
##ANOMALY DETECTIO

# defining question
#identify anomalies in the dataset

##understanding the context
#Carrefour Kenya  is one of the leading reatailsalers in the country and would like to know the most relevant strategies to put in place in order to  increase its sales. The marketing departmennt have trouble  in developing  these strategies, but working in partnership with data analyst will help alot in getting important insights from data and make informes strategies.
#Sucess metrics
# to identify any anomaly in the  dataset
---

# Installing  packages
```{r}
# intalling packages
#pkg <- c('tidyverse','tibbletime','anomalize','timetk')
#install.packages(pkg)
library(tidyverse)
library(tibbletime)
library(anomalize)
library(timetk)


```
```{r}
#loading  our data
path= "C:/Users/hp/Downloads/Supermarket_Sales_Forecasting - Sales.csv"
df <- read.csv(path)
```

```{r}
# preview data
head(df)
```

```{r}
# checking data shape 
dim(df)

```


```{r}
str(df)

```

```{r}
# check for missing values
sum(is.na(df))
```

```{r}
# Change Factor to Date format
df$Date <- paste(df$Date, "01", sep="-")
# Select only relevant columns in a new dataframe
df$Date<- as.Date(df$Date,format="%Y-%m-%d")
```

```{r}
df <- df %>% select(Date,Sales)
```

```{r}
# Convert df to a tibble
df1 <- as_tibble(df)
class(df1)
````
```{r}
# anomaly detection
df_anomalized <-tidyverse_cran_downloads %>%
    time_decompose(count) %>%
    anomalize(remainder) %>%
    time_recompose() %>%
    plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.5)

```
# there are  no anomalies present in our dataset

```{r}
df_anomalized %>% glimpse()
```


